### 2018-02-11 monograph/thesis/chapters/beautifiers.tex
Deprecated the chapter good_practices.tex and moved the CI
Continuous Integration section to beautifiers.tex

>>>>

    \section{Continuous Integration}

    TODO

    On a distributed version control system,
    continuous integration would be continuously running the system tests
    as long new code is integrated into main system
    from the distributed clients \cite{continuousIntegration}.

    \begin{enumerate}[leftmargin=*]
        \item \citeonline{trackingChanges},
        \item \footnote{\url{https://blog.codinghorror.com/check-in-early-check-in-often/}}
        \item \cite{aspectOriented}
    \end{enumerate}
